opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-06 chapters/01_introduction.tex
Added labeled column in dataset overview
Eliminated redundancy in author listing

% Manual rietveld refinement and its problems
Manually performing Rietveld refinement is time-consuming and often requires expert knowledge. It is not scalable to the degree required to keep up with advances in throughput and efficiency in other steps of the experimentation pipeline. In a Rietveld refinement process, the operator starts by setting parameters that characterize the background and peak shape of the powder diffraction pattern and determines a crystal structure model from which the optimization process can start. This model is usually obtained using search-match software, which identifies crystal structures with similar powder diffraction patterns from a database of crystal structures with accompanying powder diffraction patterns. Databases commonly used for this purpose include the Powder Diffraction File\cite{GatesRector2019}, the Inorganic Crystal Structure Database \cite{Belsky2002}, and the Crystallography Open Database \cite{Grazulis2009}. However, an initial structural model obtained from such a database via search-match software is not guaranteed to lead to an accurate structure solution through Rietveld refinement. Especially for novel structures, obtaining an initial structural model through matching to a database of known structures can be problematic. \\ %In such cases, more complex crystal structure solution approaches need to be applied to find suitable crystal structure guesses. \\

@@

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis. We hope that this can drive ML research in this field towards more advanced automated analysis workflows that can accelerate materials science research through ready application in high-throughput experimentation pipelines.

>>>>

% Manual rietveld refinement and its problems
Manually performing Rietveld refinement is time-consuming and often requires expert knowledge. It is not scalable to the degree required to keep up with advances in throughput and efficiency in other steps of the experimentation pipeline. In a Rietveld refinement process, the operator starts by setting parameters that characterize the background and peak shape of the powder diffraction pattern and determines a crystal structure model from which the optimization process can start. This model is usually obtained using search-match software, which identifies crystal structures with similar powder diffraction patterns from a database of crystal structures with accompanying powder diffraction patterns. Databases commonly used for this purpose include the Powder Diffraction File\cite{GatesRector2019}, the Inorganic Crystal Structure Database \cite{Belsky2002}, and the Crystallography Open Database \cite{Grazulis2009}. However, an initial structural model obtained from such a database via search-match software is not guaranteed to lead to an accurate structure solution through Rietveld refinement. Especially for novel structures, obtaining an initial structural model through matching to a database of known structures can be problematic. In such cases, more complex crystal structure solution approaches need to be applied to find suitable crystal structure guesses \cite{structure_solution_review}.\\

@@

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis. We hope that this can drive ML research in this field towards more advanced automated analysis workflows that can accelerate materials science research through ready application in high-throughput experimentation pipelines.\\

### 2024-12-06 chapters/02_SOTA_ML.tex
Eliminated redundancy in author listing

%\paragraph{ML for pXRD}
To showcase the need for datasets such as the one presented in this publication, we now shortly discuss some recent
approaches that apply machine learning methods to classification and regression tasks for powder diffractograms. \\

@@

A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi {\it et al} \cite{Chitturi2021}. They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles.
Zhang {\it et al.} introduce a convolutional self-attention neural network trained on simulated patterns to classify crystal types \cite{zhang2024crystallographic}. Their model was tested on 23,073 unary, binary, and ternary inorganic crystal structures sourced from the COD. The study observed a noticeable performance drop when the pre-trained model was applied to real experimental patterns, as opposed to simulated data. However, their recent work \cite{cao2024simxrd} proposes using convolutional peak descriptors that consider the detector's geometry, which significantly reduces the performance gap in their benchmark tests.\\

@@

In our 2023 paper, we developed an approach to generate synthetic crystal structures and their corresponding pXRD patterns on the fly during the training process \cite{Schopmans2023}. This approach defeats the issue of
a limited dataset size, which limits the depth of neural networks that can be trained. However, the accuracy dropped substantially when we applied our space group classification model to experimental patterns from the RRUFF database. Augmenting our simulated patterns with background, noise, and impurities helps to bring simulated diffractograms closer to experimental ones, making models trained on them more performant on experimental diffractograms. However, this augmentation process could be improved by incorporating background and noise statistics from a broader experimental pXRD database.\\

It becomes apparent, that the more general the task is, the more challenging the transfer to experimental data is. For example, the space group classification task is very general, for all material systems. Therefore, transferring it to the application on experimental diffraction patterns is difficult. \cite{Schopmans2023, Lee2022, Vecsei2018} On the other hand, there are some successful approaches that also work well on experimental data, but those are mostly methods that do phase determination in a limited compound space, making the task less complex. \cite{Schuetzke2024, Lee2020}

The ultimate goal of ML efforts is to make pXRD data identification practical for experimental use, automating structure property prediction. However, the current volume of experimental pXRD patterns is insufficient to effectively train ML models, highlighting an urgent need for a comprehensive experimental pXRD database. To address this, two key approaches are essential. First, developing more sophisticated simulation methods to better approximate experimental patterns\cite{cao2024simxrd} by using statistics from experimental diffractograms. Second, creating an experimental database that enables transfer learning to bridge the gap between simulated and real-world data. For both of these steps, the development of opXRD is particularly significant, as it will provide a comprehensive experimental benchmark for the community, allowing fair comparison of baseline models and accurate evaluation of their applicability in real experimental situations.

>>>>

\paragraph{ML for pXRD}

To showcase the need for datasets such as the one presented in this publication, we now shortly discuss some recent
approaches that apply machine learning methods to classification and regression tasks for powder diffractograms. \\

@@

A regression analysis on lattice parameters within a broader framework encompassing all material classes was conducted by Chitturi {\it et al} \cite{Chitturi2021}. They developed a distinct CNN for each crystal system, utilizing a merged dataset from both the ICSD and the Cambridge Structural Database, and managed to achieve a mean absolute percentage error of about \SI{10}{\percent} for the lattice lengths, although they encountered difficulties in accurately predicting angles.
Zhang {\it et al.} introduce a convolutional self-attention neural network trained on simulated patterns to classify crystal types \cite{zhang2024crystallographic}. Their model was tested on 23,073 unary, binary, and ternary inorganic crystal structures sourced from the COD. The study observed a noticeable performance drop when the pre-trained model was applied to real experimental patterns, as opposed to simulated data. However, their recent work \cite{cao2024simxrd} proposes using convolutional peak descriptors that consider the detector's geometry, which reduces the performance gap in their benchmark tests.\\

@@

In our 2023 paper, we developed an approach to generate synthetic crystal structures and their corresponding pXRD patterns on the fly during the training process \cite{Schopmans2023}. This approach defeats the issue of
a limited dataset size, which limits the depth of neural networks that can be trained. However, the accuracy dropped substantially when we applied our space group classification model to experimental patterns from the RRUFF database. Augmenting our simulated patterns with background, noise, and impurities helps to bring simulated diffractograms closer to experimental ones, making models trained on them more performant on experimental diffractograms. However, this augmentation process could be improved by incorporating background and noise statistics from a broader experimental pXRD database, such as the one presented in this publication.\\

It becomes apparent that the more general the task is, the more challenging the transfer to experimental data. For example, the space group classification task across all material systems is very general. Therefore, transferring it to the application on experimental diffraction patterns is difficult. \cite{Schopmans2023, Lee2022, Vecsei2018} On the other hand, there are some successful approaches that also work well on experimental data, but those are mostly methods that do phase determination in a limited compound space, making the task less complex. \cite{Schuetzke2024, Lee2020}\\

The ultimate goal of ML efforts is to make pXRD data identification practical for experimental use, automating structure prediction. However, the current volume of experimental pXRD patterns is insufficient to effectively train ML models, highlighting an urgent need for a comprehensive experimental pXRD database. Two key approaches are essential to address this. First, developing more sophisticated simulation methods to better approximate experimental patterns\cite{cao2024simxrd} by using statistics from experimental diffractograms. Second, creating an experimental database that enables transfer learning to bridge the gap between simulated and real-world data. For both of these steps, the development of opXRD is particularly significant, as it will provide a comprehensive experimental benchmark for the community, allowing fair comparison of baseline models and accurate evaluation of their applicability in real experimental situations.

### 2024-12-06 chapters/03_existing_datasets.tex
Eliminated redundancy in author listing

\subsubsection*{Existing experimental powder diffraction databases}
To contextualize opXRD within the current environment of experimental powder diffraction data, the following list provides an overview of the largest crystal structure databases that offer access to experimental powder diffraction data. For an overview of these databases refer to Tab.$\eqref{tab:exp_databases}$ below.\\

@@

\textbf{Linus Pauling File}:\cite{PaulingWeb} The Linus Pauling File is a largely commercial crystal structure database published and maintained by the Pauling File project \cite{villars2018}. It is currently distributed as Pearson Crystal data \cite{PearsonWeb} and the Materials Platform for Data Science (MPDS)\cite{MPDSWeb}. The database, first published in 2002, currently contains more than 534,000 crystal structures\cite{MPDSWeb} and 21,700 corresponding experimental powder diffraction patterns\cite{PearsonWeb}. 
This makes the Pauling file, to the best of our knowledge, the largest collection of experimental powder diffraction data available to researchers. As of November 2024, Pearson's crystal data is available to researchers through a purchase of a one-year license starting at a price point of \qty{2200}{\myeuro}. The MPDS is partially open, with the open MPDS data accessible through a web interface\cite{MPDSWeb}. Access to the full MPDS database can be purchased through a one-year license starting at \qty{2000}. \\

>>>>

\subsubsection*{Existing experimental powder diffraction databases}
To contextualize opXRD within the current environment of experimental powder diffraction data, the following list provides an overview of the largest crystal structure databases that offer access to experimental powder diffraction data. For an overview of these databases refer to Tab.$\eqref{tab:exp_databases}$ below.

@@

\textbf{Linus Pauling File}:\cite{PaulingWeb} The Linus Pauling File is a largely commercial crystal structure database published and maintained by the Pauling File project \cite{villars2018}. It is currently distributed as Pearson Crystal data \cite{PearsonWeb} and the Materials Platform for Data Science (MPDS)\cite{MPDSWeb}. The database, first published in 2002, currently contains more than 534,000 crystal structures\cite{MPDSWeb} and 21,700 corresponding experimental powder diffraction patterns\cite{PearsonWeb}. 
This makes the Pauling file, to the best of our knowledge, the largest collection of experimental powder diffraction data available to researchers. As of November 2024, Pearson's crystal data is available to researchers through a purchase of a one-year license starting at a price point of \qty{2200}{\myeuro}. The MPDS is partially open, with the open MPDS data accessible through a web interface\cite{MPDSWeb}. Access to the full MPDS database can be purchased through a one-year license starting at \qty{2000}{\myeuro}. \\

### 2024-12-06 chapters/04_our_dataset.tex
Eliminated redundancy in author listing

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\scalebox{0.92}{
\begin{tabular}{@{}clcccccl@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Unit Cell & Research Project \\ 
\midrule
CNRS        & \qquad 1052          & \cmark   & \cmark   & \cmark   & \cmark   & Extracted from the COD                 \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \cmark   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \cmark   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}}
\end{table}

>>>>

\newcommand{\partialexclam}[1]{\textcolor{orange}{\ding{52}(#1\%)}}

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\scalebox{0.92}{
\begin{tabular}{@{}clccclll@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Basis & Research Project \\ 
\midrule
CNRS        & \qquad 1052          & \cmark   & \cmark   & \cmark   &  \partialexclam{79}   & Extracted from the COD                 \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \cmark   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \cmark   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}}
\end{table}

### 2024-12-06 main.tex
Added square to citations to differentiate from footnotes
Added showing DOI as clickable links in bibliography when available
Added paragraph on Pearson's crystal data
Changed plaintext SI units/degrees into latex symbols
Warpped chemical formulas in \ce{} environemnt
Commented out statement that pearson and PDF have huge overlap
Described overlap in experimental pXRD data in PDF5+ and Pearson's Crystal data
Added dataset overview tables
Updated introductory paragraphs on rietveld refinement
Described python + zenodo data availability
Commited table version with footnote directly underneath
Ad

\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[super,sort&compress,comma]{natbib}
%\renewcommand{\supercite}[1]{\cite{#1}}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{csquotes}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage{authblk}
\usepackage{multirow}
\usepackage{nomencl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{amsfonts}
\usepackage{outlines} %%same
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{bm}
\usepackage[normalem]{ulem} %%temporary, for organization purposes

\date{}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\DeclareSIUnit\angstrom{\text {Å}}
\usepackage[final]{changes}

\interfootnotelinepenalty=10000
% Changed idea title idea from orignal title of
% "Towards a free high quality powder x-ray diffractogram database"
% Name is supposed to be in analogy with Crystallography Open database
% which is the largest freely available database of crystal structures
\title{opXRD: Open Experimental Powder X-ray Diffraction Database}

\author[1,2]{Daniel Hollarek}
\author[1,2]{Henrik Schopmans}
\author[1,2]{Jona Östreicher}
\author[2]{Simon Schweidler}
\author[3]{Adie Alwen}
\author[4]{Mriganka Singh}
\author[4,5]{Tim Kodalle}
\author[2]{Ben Breitung}
\author[11, 12]{Maged Abdelsamie}
\author[6]{Gregoire Heymans}
\author[7]{Alexander Wieczorek}
\author[7]{Siarhei Zhuk}
\author[7]{Sebastian Siol}
\author[8]{Moritz Wolf}
\author[9]{François-Xavier Coudert}
\author[9]{Arthur Hardiagon}
\author[10]{Bin Cao}
\author[13]{Ruth Schwaiger}
\author[10]{Tong-yi Zhang}
\author[4]{Carolin M. Sutter-Fella}
\author[3]{Andrea M. Hodge}
\author[1,2]{Pascal Friederich}

% I made the affiliations smaller because there's a lot of them
\renewcommand\Affilfont{\small}

\affil[1]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[2]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[3]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[4]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[5]{Lawrence Berkeley National Laboratory, Advanced Light Source, Berkeley 94720 CA, USA}
\affil[6]{Lawrence Berkeley National Laboratory, Chemical Sciences Division, Berkeley 94720 CA, USA}
\affil[7]{Empa~–~Swiss Federal Laboratories
for Materials Science and Technology, 8600 Dübendorf,
Switzerland}
\affil[8]{Engler-Bunte-Institut \& Institute of Catalysis
Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[9]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[10]{Guangzhou Municipal Key Laboratory of Materials Informatics,  Hong Kong University of
Science and Technology (Guangzhou), Guangzhou 511400, China}
\affil[11]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia}
\affil[12]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, KFUPM, Dhahran 31261, Saudi Arabia}
\affil[13]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany}
\begin{document}

@@

\newpage
\section{Introduction}\label{sec:Introduction}
\input{chapters/01_introduction}

\*section{Existing datasets}
\input{chapters/02_existing_datasets}

\*section{Machine learning for pXRD}
\input{chapters/03_SOTA_ML}

\section{opXRD database}\label{sec:our_dataset}
\input{chapters/04_our_dataset}

\section{How to contribute and how to use}\label{sec:how_to_use}
\input{chapters/05_how_to_use}

@@

\bibliography{references}
\bibliographystyle{rsc}

>>>>

\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[super,sort&compress,comma, square]{natbib}
%\renewcommand{\supercite}[1]{\cite{#1}}

%% Language and font encodings
\usepackage{tikz}
\usepackage{tablefootnote}
\usepackage{gensymb}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{doi}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage{authblk}
\usepackage{multirow}
\usepackage{nicematrix,enumitem,booktabs}
\usepackage{nomencl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{amsfonts}
\usepackage{outlines} %%same
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\usepackage{eurosym}
\usepackage[locale = DE]{siunitx}
\usepackage{bm}
\usepackage[normalem]{ulem} %%temporary, for organization purposes
\usepackage{pythonhighlight}
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\textcolor{green!80!black}{\ding{52}}}
\newcommand{\xmark}{\textcolor{red}{\ding{53}}}

\date{}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\DeclareSIUnit{\myeuro}{\text{\euro}}
\DeclareSIUnit\angstrom{\text {Å}}
\usepackage[final]{changes}

\interfootnotelinepenalty=10000
\title{opXRD: Open Experimental Powder X-ray Diffraction Database}

\newcommand{\ITI}{1}
\newcommand{\INT}{2}
\newcommand{\HKUSTGZ}{3}
\newcommand{\USC}{4}
\newcommand{\LBLMF}{5}
\newcommand{\LBLALS}{6}
\newcommand{\Hoffmann}{7}
\newcommand{\LBLCS}{8}
\newcommand{\EMPA}{9}
\newcommand{\KITICRT}{10}
\newcommand{\CPT}{11}
\newcommand{\KFUPMMSE}{12}
\newcommand{\KFUPMIRCIMR}{13}
\newcommand{\FZJIEMD}{14}

\author[\ITI,\INT]{Daniel Hollarek}
\author[\ITI,\INT]{Henrik Schopmans}
\author[\INT]{Jona Östreicher}
\author[\HKUSTGZ]{Bin Cao}
\author[\INT]{Simon Schweidler}
\author[\USC]{Adie Alwen}
\author[\LBLMF]{Mriganka Singh}
\author[\LBLMF,\LBLALS]{Tim Kodalle}
\author[\Hoffmann]{Hanlin Hu}
\author[\LBLCS]{Gregoire Heymans}
\author[\EMPA]{Alexander Wieczorek}
\author[\EMPA]{Siarhei Zhuk}
\author[\CPT]{Arthur Hardiagon}
\author[\KFUPMMSE,\KFUPMIRCIMR]{Maged Abdelsamie}
\author[\HKUSTGZ]{Tong-yi Zhang}
\author[\USC]{Andrea M. Hodge}
\author[\FZJIEMD]{Ruth Schwaiger}
\author[\INT]{Ben Breitung}
\author[\EMPA]{Sebastian Siol}
\author[\KITICRT]{Moritz Wolf}
\author[\CPT]{François-Xavier Coudert}
\author[\LBLMF]{Carolin M. Sutter-Fella}
\author[\ITI,\INT]{Pascal Friederich}

\renewcommand\Affilfont{\small}

\affil[\ITI]{Institute of Theoretical Informatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[\INT]{Institute of Nanotechnology, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
\affil[\USC]{Department of Chemical Engineering and Materials Science, University of Southern California, Los Angeles CA 90089, USA}
\affil[\LBLMF]{Lawrence Berkeley National Laboratory, Molecular Foundry Division, Berkeley 94720 CA, USA}
\affil[\LBLALS]{Lawrence Berkeley National Laboratory, Advanced Light Source, Berkeley 94720 CA, USA}
\affil[\Hoffmann]{Hoffmann Institute of Advanced Materials, Shenzhen Polytechnic, Shenzhen 518055, China}
\affil[\LBLCS]{Lawrence Berkeley National Laboratory, Chemical Sciences Division, Berkeley 94720 CA, USA}
\affil[\EMPA]{Empa–Swiss Federal Laboratories for Materials Science and Technology, 8600 Dübendorf, Switzerland}
\affil[\KITICRT]{Engler-Bunte-Institut \& Institute of Catalysis Research and Technology, Karlsruhe Institute of Technology, Karlsruhe, Germany}
\affil[\CPT]{Chimie ParisTech, PSL University, CNRS, Institut de Recherche de Chimie Paris, 75005 Paris, France}
\affil[\HKUSTGZ]{Guangzhou Municipal Key Laboratory of Materials Informatics, Hong Kong University of Science and Technology (Guangzhou), Guangzhou 511400, China}
\affil[\KFUPMMSE]{Material Science and Engineering Department, King Fahd University of Petroleum and Minerals (KFUPM), Dhahran 31261, Saudi Arabia}
\affil[\KFUPMIRCIMR]{Interdisciplinary Research Center for Intelligent Manufacturing and Robotics, KFUPM, Dhahran 31261, Saudi Arabia}
\affil[\FZJIEMD]{Institute of Energy Materials and Devices, Forschungszentrum Juelich GmbH, 52425 Juelich, Germany}

\begin{document}

@@

\newpage
\section{Introduction}\label{sec:Introduction}
\input{chapters/01_introduction}
\input{chapters/02_SOTA_ML}

\section{Existing datasets}
\input{chapters/03_existing_datasets}

\pagebreak
\section{opXRD database}\label{sec:our_dataset}
\input{chapters/04_our_dataset}

\section{Usage}\label{sec:how_to_use}
\input{chapters/05_how_to_use}

\section{Summary and Outlook}\label{sec:summary_and_outlook}
\input{chapters/06_summary_and_outlook}

@@

\bibliographystyle{bibstyle/bibstyle.bst}
\bibliography{references}
